Quantum Mechanics Enabled Genetic Programming\\

### 2020-09-23 paper_nit.tex
23_09_report_1

The field of applied quantum mechanics is still unexplored for the best part. However, there are certain applications in which QC outperforms CC. Consider Shor's algorithm and RSA, both of which are used for encryption. The encryption of any form of data transmitted over the Internet relies immensley on factorization of a huge number. This process is extremley ardous for a non-quantum computer, with the best known factoring technique requiring an amount of time proportional to 2$\textsuperscript{n\textsuperscript{\sufr{1}{3}}log(n)\textsuperscript{\sufr{2}{3}}}$ 
, where $\textit{n}$ is the number of digits in the number to be factored.

>>>>

The field of applied quantum mechanics is still unexplored for the best part. However, there are certain applications in which QC outperforms CC. Consider Shor's algorithm and RSA, both of which are used for encryption. Basically, the encryption of any form of data transmitted over the Internet relies immensley on factorization of a huge number. This process is extremley ardous for a non-quantum computer, with the best known factoring technique requiring an amount of time proportional to 2$\textsuperscript{n\textsuperscript{\sufr{1}{3}}log(n)\textsuperscript{\sufr{2}{3}}}$ 
, where $\textit{n}$ is the number of digits in the number to be factored. Meanwhile Shor's Quantum algorithm requires time proportional to only $n\textsuperscript{2}log(n)log(log(n))$.

QC takes advantage of major quantum phenomena such as superposition, quantum entanglment, principle of uncertainity among others, for improving existing searchc and optimization techniques. Humans inherently stick to definitive physical concepts such as deterministic state transition, state duality and temporal static behaviour of particles.

According to Moore's Law, the size of computational units shrinks at an exponential rate as the number of transistors on a chipset increases every year. Even after accounting for physical constraints, a time will come when operations will be conducted on an atomic scale. On such a level, atomic forces overpower particle physics naturally. As a result, understanding QC and applying them in a virtual landscape to get a sense of their possibilities is a must.

\subsection{Using Evolutionary Algorithms}

Evolutionary Algorithms (EA) encompass a wide array of research ideas stemming from general principles of genetics and the theory of evolution. Models are developed to illustrate the behaviour of naturally occuring phenomena, develop these algorithms and test out the application of the corresponding theory. The general process of any EA is depicted in figure \ref{p1}. In a nutshell, an initial population of candidate solutions is generated and each solution is labelled according to their performance on a set fitness function. Further down the line, these candidates are improved upon by conducting a set of operations on them for a predetermined number of generations. After some stopping criterias are achieved, the process strops and the best candidate is hypothesized as the global solution. The advantages offered by this technqiue include but not limited to resilience to noise, in-built support for parallelism and distributed learning, multi-pronged attack and handling complex problems.

\begin{figure}[!b]
\centering\includegraphics[height=6.75cm]{p1.png}
\caption{General Flow of Evolutionary Algorithms}
\label{p1}
\end{figure}

Our paper provides an insight into the ensemble of both the previously mentioned techniques and preparing algorithms for a future where quantum computers replace traditional computers as commonplace machines.
